Discrete Quantum Theories and Computing

### 2019-02-04 dissertation.tex
dissertation.lyx Acknowledgments Adding a table...

\usepackage{tabularx}
\renewcommand{\tabularxcolumn}[1]{m{#1}}
\newcolumntype{Y}{>{\centering\doublespacing\arraybackslash}X}
\newcolumntype{M}[1]{>{\centering\doublespacing\arraybackslash}m{\widthof{#1}}}

@@

\caption{\label{tab:acknowledgments}I want to thank the professors co-authored
with me, suggested me as a committee member, and taught me, and the
collaboration or supervised works or studies become the basis of or
inspire this dissertation.}

@@

I want to thanks all my professors co-authored with me, suggested
me as a committee members, and taught me so that our work or studies
became the bases or inspired any part of my dissertation as listed
in Table~\ref{tab:acknowledgments}. Especially, Prof.\ Andrew J.
Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})

@@

To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Also, the unpublished computation
for the discrete Deutsch algorithm \cite{Deutsch1985,544199,Mermin2007}
is organized in the term paper for SLST-T501 Academic Writing course.
I want to thank Prof.\ Tom Lewis for proof-reading them, and they
become the bases of Sec.~\ref{subsec:Discrete-Deutsch-algorithm}.
Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Prof.\ Huah Chu (朱樺), Weihua Liu (刘伟华), Caren Liu
(劉鈺平), Meng-Wei Chen (陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen
(陳昭宏)\ldots , etc. This could be listed on and on. I still thank
you even if your name is not listed here, and sorry for my bad memory.

@@

Our computations with this ``toy'' modal quantum theory showed that
it possesses ``supernatural'' computational power. For example,
one can solve a black box version of the \usat\ problem~\cite{usat}
in a way that outperforms conventional quantum computing. The classical
\usat\ problem (also known as $\lang{USAT}$ or $\lang{UNAMBIGUOUS-SAT}$)
\begin{comment}
\todo{Add citation about where these two names come from. }
\end{comment}
is the problem of deciding whether a given Boolean formula has a satisfying
assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
This problem is, in a precise sense~\cite{Valiant198685}, just as
hard as the general satisfiability problem and hence all problems
in the $\NP$ complexity class. Our black-box version of the \usat\ problem
replaces the Boolean formula with an arbitrary black box. Solutions
to this generalized problem can be used to solve an unstructured database
search of size $N$ using $O\left(\log N\right)$ black box evaluations
by binary search on the database. This algorithm then outperforms
the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
database search in conventional quantum computing.

>>>>

% https://wiki.lyx.org/LyX/Tables#tabularx
%% Hack by Heiko Oberdiek (on de.comp.text.tex)
\usepackage{tabularx}

%% Redefine the standard table
\let\ORIGtabular\tabular
\let\ORIGendtabular\endtabular
\let\ORIGtabularx\tabularx
\renewcommand*{\tabularx}{%
  \def\tabular{%
    \let\endtabular\ORIGendtabular
    \ORIGtabular
  }%
  \ORIGtabularx
}

\renewcommand{\tabularxcolumn}[1]{m{#1}}
\newcolumntype{Y}{>{\centering\doublespacing\arraybackslash}X}
\newcolumntype{M}[1]{>{\centering\doublespacing\arraybackslash}m{\widthof{#1}}}

@@

\caption{\label{tab:committee}I want to thank the professors co-authored with
me, suggested me as a committee member, and taught me, and the collaboration
or supervised works or studies become the basis of or inspire this
dissertation.}

@@

I want to thanks the professors served in all my committees. These
professors advised me as committee members and taught me while we
wrote papers together and when I took their courses. Most of my dissertation
is either based on these papers or inspired by the studies supervised
by them as listed in Table~\ref{tab:committee}. Especially, Prof.\ Andrew
J. Hanson, Prof.\ Gerardo Ortiz, and Prof.\ Amr A. Sabry\ (\textarabic{عمرو صبري})

@@

\begin{sidewaystable}
\noindent \begin{centering}
\caption{\label{tab:teacher}The knowledge I learned from teachers in other
courses help me consolidate this dissertation, where IUB stands for
Indiana University Bloomington and NTU stands for National Taiwan
University.}
\par\end{centering}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{ccM{MATH-M522}M{English~for~International~Graduate~Students:}Y}
\toprule 
\addlinespace
Instructor & School & Course & Title & Relation with the dissertation\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule 
\addlinespace
Tom Lewis & IUB & SLST-T501 & English for International Graduate Students:\linebreak[3] Academic
Writing & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Michael A. Mandell & IUB & MATH-M522 & Topology II & The textbook~\cite{Hatcher2001} is cited in Chapters~\ref{chap:Introduction}
and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Valery Lunts & IUB & MATH-M501 & Survey of Algebra & The textbook~\cite{DummitFoote2004} is cited in Sec.~\ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Huah Chu (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & Algebra(I)\linebreak[3] Algebra(II) & The textbook~\cite{Artin1991} is cited in Sec.~\ref{CQC1qubitBloch.sec},
\ref{sec:background}, \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{sidewaystable}
To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Besides of my committee members,
the knowledge I learned from teachers in other courses help me consolidate
this dissertation as listed in Table~\ref{tab:teacher}.

Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
could be listed on and on. I still thank you even if your name is
not listed here, and sorry for my bad memory.

@@

Our computations with this ``toy'' modal quantum theory showed that
it possesses ``supernatural'' computational power. For example,
one can solve a black box version of the \usat\ problem~\cite{usat}
in a way that outperforms conventional quantum computing. The classical
\usat\ problem (also known as $\lang{USAT}$~\cite{AroraBarak2009}
or $\lang{UNAMBIGUOUS-SAT}$) %
\begin{comment}
\todo{Add citation about where these two names come from. }
\end{comment}
is the problem of deciding whether a given Boolean formula has a satisfying
assignment, assuming that it has at most one such assignment~\cite{Papadimitriou1993}.
This problem is, in a precise sense~\cite{Valiant198685}, just as
hard as the general satisfiability problem and hence all problems
in the $\NP$ complexity class. Our black-box version of the \usat\ problem
replaces the Boolean formula with an arbitrary black box. Solutions
to this generalized problem can be used to solve an unstructured database
search of size $N$ using $O\left(\log N\right)$ black box evaluations
by binary search on the database. This algorithm then outperforms
the known asymptotic bound $O\left(\sqrt{N}\right)$ for unstructured
database search in conventional quantum computing.
